\thesistitle

### 2019-07-29 sections/clonerefactor.tex
Fixes

To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration:

\begin{equation}\label{eq:sameclass}
\text{a clone instance I is considered ``Method Level'' iff \forall (n \in I)\text{ } Tn = ``MethodDeclaration'' \lor \exists (p \in ancestors(n)) \text{ } Tp = ``MethodDeclaration'' }
\end{equation}

@@

>>>>

To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration. A clone instance is considered ``Method Level'' if:

\begin{equation}\label{eq:sameclass}
\forall (n \in I)\text{ } Tn = \text{ MethodDeclaration } \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{ MethodDeclaration }
\end{equation}

@@

\subsubsection{Class Level Clones}
